Do fast stellar centroiding methods saturate the Cram\'{e}r-Rao lower bound?

### 2017-06-14 ms/revision2/main.tex
adding more words to Poisson likelihood

The optimal estimator of flux is the matched-filter flux estimator 
$\tilde{F}=\sum_{i}y_{i}P_{i}$. It can be shown that 
\beq
p(\tilde{F}) = \mathcal{N}(F , \frac{\sigma^{2}}{\sum_{i}P_{i}^{2}}),
\eeq  
which leads us to
\beq
\begin{array}{l}
\text{SNR} = \frac{F\sqrt{\sum_{i} P_{i}^{2}}}{\sigma}.
\end{array}
\label{snr}
\eeq

@@

>>>>

%The optimal estimator of flux is the matched-filter flux estimator 
\todo{The optimal estimator of flux is proportional to the matched-filter flux
$\tilde{F}=\sum_{i}y_{i}P_{i}/\sum_{i}P_{i}^{2}$.} It can be shown that 
\beq
p(\tilde{F}) = \mathcal{N}(F , \frac{\sigma^{2}}{\sum_{i}P_{i}^{2}}),
\eeq  
which leads us to
\beq
\begin{array}{l}
\text{SNR} = \frac{F\sqrt{\sum_{i} P_{i}^{2}}}{\sigma}.
\end{array}
\label{snr}
\eeq

@@

The optimal estimator of flux in this case, is given by
\beq
F^{\star} = \frac{\sum_i \Big(y_i - gb\Big)P_i}{\sum_i gP_i^2}.
\label{eq:optimalf}
\eeq
SNR is the ratio of the mean and variance of the distribution function that $F^{\star}$ is drawn from. Combining Eqs.~\ref{eq:poisson_likelihood} and~\ref{eq:optimalf}, one can show that the SNR is given by 
\beq
\text{SNR} = \frac{F\sqrt{\sum_i P_i^2}}{\sqrt{\sum_i(FP_i+b)}}
\eeq

Following the assumptions of previous section: normalized flux and correctly subtracted background sky, we have

\beq
\text{SNR} = \frac{2(\beta-1)(2^{1/\beta}-1)^{1/2}}{\pi^{1/2}(2\beta-1)^{1/2}}\frac{1}{\gamma}.
\label{snr3}
\eeq
